Looking Back: One Year HPC Certification Forum

### 2019-04-11 paper.tex
Further

\usepackage{cleveref}

\usepackage{graphicx}
\graphicspath{{./fig/}}
\DeclareGraphicsExtensions{.png,.pdf,.jpg,.jpeg}

@@

This lightning talk describes the current status of the certification program and the effort to create an independent body that curate the competences and issue certificates for the users.

The foundation for this work was laid with the Performance Conscious HPC (PeCoH) project, which among other goals, aims to establish an HPC certification program.
A white paper about the approach containing technical details is provided in \cite{whitepaper}.
Within the project it become quickly apparent that the local effort is useful for the wider HPC community and could be extended to a global effort.

@@

\section{Related Work}

@@

The individual skills are organized into a tree that shows generic competences close to the root and refined skills on the leafs.
The two top-levels of the skill tree are shown in \Cref{f_top_level_competences}; we have identified more than 35 skills.
In respect to the granularity, we expect the basic level of a leaf like “Bash programming” can be acquired by novel users in a workshop day.
The tree serves the purpose of navigating across the skills, and at the same time a parent node defines the scope of its children.
For example, the \textit{USE} competence provides means of using the HPC environment to perform various tasks, such as running parallel applications, using core services of the operating system.
While the tree structure has been chosen as a graphical representation, some competences are cross-referenced, particularly in the skills of the USE branch.
The tree is managed in an XML file and we offer tools to visualize the skills as mindmap or embed them into a webpage -- more information are found in \cite{whitepaper}.

>>>>

\usepackage{cleveref}
\usepackage{todonotes}
\usepackage{graphicx}
\graphicspath{{./fig/}}
\DeclareGraphicsExtensions{.png,.pdf,.jpg,.jpeg}

\newcommand{\jk}[1]{\todo[inline]{TODO: #1}}

@@

This article describes the current status of the certification program by looking back for the one year of this independent body that curate the competences and aims to issue certificates for the users.

Our previous work described the evolution from the bootstraping project towards the independent body of the HPC Certification forum \cite{TAHCPKHHSS19}.

@@

\section{Related Work}
\jk{Please everyone!}

@@

The individual skills are organized into a tree that shows generic competences close to the root and refined skills on the leafs.
The two top-levels of the skill tree are shown in \Cref{f_top_level_competences}; we have identified more than 35 skills.
In respect to the granularity, we expect the basic level of a leaf like “Bash programming” can be acquired by novel users in a workshop day.
The tree serves the purpose of navigating across the skills, and at the same time a parent node defines the scope of its children.
For example, the \textit{USE} competence provides means of using the HPC environment to perform various tasks, such as running parallel applications, using core services of the operating system.
While the tree structure has been chosen as a graphical representation, some competences are cross-referenced, particularly in the skills of the USE branch.
The tree is managed in an XML file and we offer tools to visualize the skills as mindmap or embed them into a webpage.
